### 2018-03-07 chapter2/ms.tex
Second Pass at Ch2 Refs

Extensive theoretical and observational work has been performed to understand the potential EM emission from a merging compact object binary. The range of potential counterparts covers the entire EM spectrum. The most popular counterpart is a short-hard gamma-ray burst \citep[SGRB; e.g.,][]{Paczynski1986,Narayan+92,Berger2014} powered by rapid accretion onto the compact remnant which leads to a strongly beamed relativistic jet. The evidence for a connection between SGRBs and compact object mergers includes the association with older stellar populations than for long GRBs \citep{Berger+05,Bloom+06,Berger2011,Fong+11,Fong+13}, large physical offsets between the burst locations and their host galaxies indicative of progenitor kicks \citep{Fong+10, FongBerger13}, weak association with the underlying stellar light of their hosts \citep{Fong+10, FongBerger13}, and a lack of association with supernovae \citep{Fox+05,Soderberg+06,Berger2010,FongBerger2013,Berger2014}. The relativistic jet can also be observed in the x-ray, optical, and radio as non-thermal afterglow emission arises from interaction with the ambient medium. This emission is also affected by relativistic beaming but may still be seen off-axis as the jet decelerates and expands. In particular, for large off-axis angles $(\theta\gtrsim 2 \theta_j)$ the emission will be most pronounced in the radio on timescales of weeks to years \citep{NakarPiran11,MetzgerBerger12}.

The merger of a compact object binary involving at least one NS is also expected to produce mildly relativistic neutron-rich ejecta, with a typical mass of $M_{{\rm ej}} \sim 10^{-3}-10^{-1}\; M_{\odot}$ and a velocity of $\beta_{{\rm ej}} \sim 0.1-0.3$ \citep[see e.g.,][]{Rosswog+99,Rosswog05,Bauswein+13a}. At later times, less neutron-rich outflows may arise from the resulting accretion disk, but the mass and composition will depend sensitively on the nature of the remnant \citep[see e.g.,][]{Metzger+09a,Dessart+09,FernandezMetzger13,Fernandez+14}. The dynamical ejecta is of particular interest when studying potential EM counterparts since it is expected to produce an isotropic quasi-thermal transient powered by the radioactive decay of heavy elements produced via {\em r}-process nucleosynthesis in the neutron-rich merger ejecta \citep{LP98,Rosswog05,Metzger+10,Grossman+14,Tanaka+14}. The low ejecta mass and high ejecta velocity combined with the resulting {\em r}-process opacities \citep[$\kappa \sim 10-100 \; \text{cm}^2 \text{ g}^{-1} \text{ for } \lambda \sim 0.3 - 3\; \mu\text{m}$,][]{Kasen+13} produces a significant suppression of bluer optical emission, resulting in a faint $(L \sim 10^{40}$ erg s$^{-1} \text{ at peak})$, rapid $(t \sim$ a few days), and extremely red transient with a peak at $\sim1.5$ microns \citep[see e.g.,][]{Kasen+13,BarnesKasen13,TanakaHotokezaka13}, dubbed a ``kilonova." On longer timescales (e.g., $\sim$ years), the ejecta will decelerate via interaction with the ambient medium producing long-lasting isotropic emission in the radio \citep{NakarPiran2011}.

@@

\subsection{Kilonovae}
\label{sec:ch2_kilo}
As discussed in Section~\ref{sec:ch2_intro}, the merger of NS-NS or NS-BH binaries is expected to produce a faint, rapidly-evolving optical/NIR transient powered by the radioactive decay of {\em r}-process elements formed in the ejecta. From a wide range of simulations it has been shown that the ejecta have a typical mass range of $\Mej \sim 10^{-3}-10^{-1} \; M_{\odot}$ with velocities of $\beta_{\text{ej}} \sim 0.1-0.3$, which depend on the initial mass asymmetry in the binary \citep{Rosswog+99,Rosswog05,Bauswein+13a,Rosswog+13,PiranNakar13}. The ejecta are expected to be neutron-rich, with typical electron fractions of $Y_e \lesssim 0.1$ \citep{Metzger+10}.

@@

We use the models of \citet{Dabhra+10} to compute \emph{i} and \emph{z}-band light curves using the same methodology as in Section~\ref{sec:ch2_WDmerge}. The effective blackbody temperature has an assumed fiducial value of $T_p \approx 5800$ K from the models of \citet[see their Figure 3]{Dabhra+10}. The resulting bolometric corrections are therefore $m_{\text{bol}} - m_{\text{i}} \approx -1.9$ mag and $m_{\text{bol}} - m_{\text{z}} \approx -2.2$ mag. We assume that these corrections are constant in time and apply them to the bolometric light curves to generate $i$- and $z$-band light curves (Figure 2).

@@

\subsection{AGN Variability}
\label{sec:ch2_agns}
We also consider short-duration optical variability from active galactic nuclei (AGNs). AGN typically show strong variability on month or year-long timescales, making AGN outbursts too long in duration to be confused with a kilonovae. However, recent work has detected rare cases of day-long  or shorter variability in the NIR. \citet{Genzel+03} observed an H-band flare in Sgr A$^{*}$ during which the source brightened by a factor of 5. This flare lasted $\sim$ 30 min, with a characteristic rise time of $\sim2-5$ min. Such short timescale flares can be ruled out as kilonova contaminants by requiring a detection on more than a single night. Flares with longer durations are also unlikely to be significant contaminants. \citet{Totani+05} performed {\em V}- and {\em i}-band observations of six AGN, selected on the basis of their variability, over a period of four days. They found typical variability of only $\sim1-5\%$ above their host galaxy luminosity. More recent work by \citet{Ruan+012} studied the variability of a sample of \fermi selected blazars. They found that these sources showed a typical rms variability of $\sim0.6$ mag on timescales of $\sim 10$ d. Therefore, AGN are unlikely to exhibit sufficiently large variability to be confused with a kilonova.

@@

So far, we have only considered kilonova models affected by the large opacities of r-process heavy nuclei. We now consider the effects of modifications to the standard kilonova models and their impact on our detectability results. The key issue in determining the nature of kilonova emission is the electron fraction, $Y_e$. The value of $Y_e$ in the dynamical ejecta and from accretion disk winds is low $(Y_e \lesssim 0.2)$ which leads to the production of r-process nuclei and strong suppression of the optical emission. However, if the electron fraction of the ejecta is above the critical value of $Y_e \approx 0.25$, r-process nucleosynthesis is not able to produce heavy elements \citep[particularly the lanthanides][]Kasen+15]. The resulting opacities will be closer to those from the Fe-peak elements, leading to a bluer transient. Here we investigate speculative scenarios that could produce a ``blue" kilonova component and assess their impact on {\em r}-band detectability.

@@

Recent work by \citet{Fernandez+15} found that the amount of ejected mass is a function of the spin of the remnant black hole, with more rapidly spinning black holes leading to higher ejecta masses by a factor of several. Furthermore, they found that $Y_{{\rm e}}$ increased monotonically with black hole spin due to an increased early-time neutrino luminosity from a rapidly spinning black hole. They found that in the most extreme cases $(a \gtrsim 0.8)$, the system could eject $\sim10^{-5} - 3\times10^{-3}\;M_{\odot}$ of material with $Y_{{\rm e}} \gtrsim 0.25$. Specifically, an ejecta mass of $\sim10^{-3}\;M_{\odot}$ will produce a blue component in the kilonovae light curve with $\nu L_{\nu} \approx 7.5\times10^{40}$ erg s$^{-1}$ at $\sim6500$ \AA ($r \approx 22.5$ mag at 200 Mpc) and a peak time of $\lesssim$ 1 day \citep{Kasen+15}. This is significantly brighter in $r$-band than the kilonovae models discussed previously, but the short timescales make observing this component challenging.

\subsection{A Long-Lived Hyper-massive Neutron Star}
\label{sec:ch2_HMNS}
Another modification can be caused by a  surviving hyper-massive neutron star (HMNS). The HMNS is a potential result of NS-NS mergers, but in simulations it often collapses rapidly $(t \lesssim 100$ ms) to form a black hole \citep{Sekiguchi+11}. The prompt formation of a black hole is an implicit assumption in the kilonova models discussed so far in this paper. However, if the total mass of the binary is less than a critical value, the HMNS can survive for a longer period of time \citep{Bauswein+13a,Kaplan+13}. In this scenario, the resulting neutrino luminosity will raise the electron fraction of the disk wind ejecta and will suppress r-process nucleosynthesis. Thus, the lanthanide-free disk wind material will produce a brighter, bluer, and shorter lived component in the kilonova light curve \citep[see e.g.,][and references therein]{MetzgerPiro14,MetzgerFernandez14}. This emission component will have a strong viewing angle dependence, with the polar regions being more strongly irradiated by neutrinos than the equatorial regions which will remain obscured by lanthanide-rich material. Consequently, the blue early component is more pronounced when the merger is observed along the polar axis.

@@

\subsection{A Neutron Precursor}
\label{sec:ch2_neutronpre}
Lastly, we consider the case in which a small fraction of the neutron-rich ejecta is expanding so rapidly that it avoids the initial phase of {\em r}-process nucleosynthesis. This effect has been seen in several general relativistic simulations \citep{Bauswein+13b,Goriely+14,Just+14}. In particular, \citet{Bauswein+13b} found that for a small fraction of the ejecta $(\sim 10^{-5} - 10^{-4}\; M_{\odot})$, the expansion timescale was sufficiently rapid $(\lesssim 5$ ms) that they evade neutron capture. These neutrons will undergo $\beta$-decay and release energy into the ejecta. Given that the photon diffusion time is on the order of a few hours in the outer layers of the ejecta, a significant fraction of this energy will manage to produce radiation. The light curves of this ``neutron precursor" were modeled by \citet{Metzger+15}. They found that the $\beta$-decay from the population of free neutrons at the leading edge of $10^{-4}\;M_{\odot}$ of ejecta can produce a transient with a timescale of $\sim1-2$ hours and a peak {\em r}-band magnitude of $\approx 22.2$ mag at 200 Mpc.

@@

\begin{deluxetable}{cccccccccc}
\tabletypesize{\footnotesize}
\tablecolumns{9} 
\tabcolsep0.05in\footnotesize
\tablewidth{0pt}  
\tablecaption{Follow-up Capabilities of Wide-Field Telescopes}
\tablehead{\multicolumn{3}{c}{} & \multicolumn{2}{c}{{\em r}-band} & \multicolumn{2}{c}{{\em i}-band} & \multicolumn{2}{c}{{\em z}-band} & \multicolumn{1}{c}{} \\
\colhead{Instrument} & \colhead{FoV} & \colhead{Etendue} & \colhead{Exp.} & \colhead{Rate}  & \colhead{Exp.}  &\colhead{Rate} & \colhead{Exp.} & \colhead{Rate} &  \colhead{$i + z$ Rate} \\
\colhead{} & \colhead{(deg$^2$)} & \colhead{(m$^2$ deg$^2$)} & \colhead{(s)} & \colhead{(deg$^2$ hr$^{-1}$)} & \colhead{(s)} & \colhead{(deg$^2$ hr$^{-1}$)} & \colhead{(s)} & \colhead{(deg$^2$ hr$^{-1}$)} &  \colhead{(deg$^2$ hr$^{-1}$)}}
\startdata
DECam$^{{\rm a}}$ & 3 &  37.7 & 4200 & 2.5 & 250 & 43 & 150 & 72 & 27  \\
ZTF$^{{\rm b}}$ & 47 & 53.2 & $9\times10^5$  & 0.2 & 1.6$\times10^4$ & 10 & {\bf --} & {\bf --}  & {\bf --}   \\
Subaru HSC$^{{\rm c}}$  & 1.8  & 90.5 & 520 & 12 & 55 & 115 & 45 & 145 & 65 \\
Pan-STARRS2$^{{\rm d}}$ & 14 & 35.6 & $1.4\times10^4$  & 4 & 700  & 72 & 350 & 144  & 30 \\
LSST$^{{\rm e}}$ & 9.6 & 315 & 390 & 88 & 28 & 1235  & 19 & 1820 & 735
\enddata
\tablecomments{Expected rates of sky coverage in deg$^2$ hr$^{-1}$ for several existing and future wide-field facilities at a depth of $r\approx26$ mag, $i\approx24$ mag and $z\approx23$ mag (i.e., the depths necessary to achieve a 95\% detection rate for kilonovae). We note that for HSC and LSST we include overhead times of 20s and 2s, respectively, as they are comparable to the exposure times. 
References: \begin{enumerate}[label=\alph*,topsep=5pt]
\item DECam ETC, \url{http://www.ctio.noao.edu/noao/content/Exposure-Time-Calculator-ETC-0}
\item \citet{Nissanke+13,Bellm2014,KasliwalNissanke14}
\item HSC ETC, \url{http://www.naoj.org/cgi-bin/img_etc.cgi}
\item Pan-STARRS DRM, \url{http://pan-starrs.ifa.hawaii.edu/}
\item LSST ETC, \url{http://dls.physics.ucdavis.edu:8080/etc4_3work/servlets/LsstEtc.html}
\end{enumerate}
}
\label{tab:ch2_tele}
\end{deluxetable}

>>>>

Extensive theoretical and observational work has been performed to understand the potential EM emission from a merging compact object binary. The range of potential counterparts covers the entire EM spectrum. The most popular counterpart is a short-hard gamma-ray burst \citep[SGRB; e.g.,][]{Paczynski1986,Narayan+92,Berger2014} powered by rapid accretion onto the compact remnant which leads to a strongly beamed relativistic jet. The evidence for a connection between SGRBs and compact object mergers includes the association with older stellar populations than for long GRBs \citep{Berger+05,Bloom+06,Berger2011,Fong+11,Fong+13}, large physical offsets between the burst locations and their host galaxies indicative of progenitor kicks \citep{Fong+10, FongBerger13}, weak association with the underlying stellar light of their hosts \citep{Fong+10, FongBerger13}, and a lack of association with supernovae \citep{Fox+05,Soderberg+06,Berger2010,FongBerger13,Berger2014}. The relativistic jet can also be observed in the x-ray, optical, and radio as non-thermal afterglow emission arises from interaction with the ambient medium. This emission is also affected by relativistic beaming but may still be seen off-axis as the jet decelerates and expands. In particular, for large off-axis angles $(\theta\gtrsim 2 \theta_j)$ the emission will be most pronounced in the radio on timescales of weeks to years \citep{NakarPiran11,MetzgerBerger12}.

The merger of a compact object binary involving at least one NS is also expected to produce mildly relativistic neutron-rich ejecta, with a typical mass of $M_{{\rm ej}} \sim 10^{-3}-10^{-1}\; M_{\odot}$ and a velocity of $\beta_{{\rm ej}} \sim 0.1-0.3$ \citep[see e.g.,][]{Rosswog+99,Rosswog2005,Bauswein+13a}. At later times, less neutron-rich outflows may arise from the resulting accretion disk, but the mass and composition will depend sensitively on the nature of the remnant \citep[see e.g.,][]{Metzger+09a,Dessart+09,FernandezMetzger13,Fernandez+15}. The dynamical ejecta is of particular interest when studying potential EM counterparts since it is expected to produce an isotropic quasi-thermal transient powered by the radioactive decay of heavy elements produced via {\em r}-process nucleosynthesis in the neutron-rich merger ejecta \citep{LP98,Rosswog2005,Metzger+10,Grossman+14,Tanaka+14}. The low ejecta mass and high ejecta velocity combined with the resulting {\em r}-process opacities \citep[$\kappa \sim 10-100 \; \text{cm}^2 \text{ g}^{-1} \text{ for } \lambda \sim 0.3 - 3\; \mu\text{m}$,][]{Kasen+13} produces a significant suppression of bluer optical emission, resulting in a faint $(L \sim 10^{40}$ erg s$^{-1} \text{ at peak})$, rapid $(t \sim$ a few days), and extremely red transient with a peak at $\sim1.5$ microns \citep[see e.g.,][]{Kasen+13,BarnesKasen13,TanakaHotokezaka13}, dubbed a ``kilonova." On longer timescales (e.g., $\sim$ years), the ejecta will decelerate via interaction with the ambient medium producing long-lasting isotropic emission in the radio \citep{NakarPiran11}.

@@

\subsection{Kilonovae}
\label{sec:ch2_kilo}
As discussed in Section~\ref{sec:ch2_intro}, the merger of NS-NS or NS-BH binaries is expected to produce a faint, rapidly-evolving optical/NIR transient powered by the radioactive decay of {\em r}-process elements formed in the ejecta. From a wide range of simulations it has been shown that the ejecta have a typical mass range of $\Mej \sim 10^{-3}-10^{-1} \; M_{\odot}$ with velocities of $\beta_{\text{ej}} \sim 0.1-0.3$, which depend on the initial mass asymmetry in the binary \citep{Rosswog+99,Rosswog2005,Bauswein+13a,Rosswog+13}. The ejecta are expected to be neutron-rich, with typical electron fractions of $Y_e \lesssim 0.1$ \citep{Metzger+10}.

@@

We use the models of \citet{Darbha+10} to compute \emph{i} and \emph{z}-band light curves using the same methodology as in Section~\ref{sec:ch2_WDmerge}. The effective blackbody temperature has an assumed fiducial value of $T_p \approx 5800$ K from the models of \citet[see their Figure 3]{Darbha+10}. The resulting bolometric corrections are therefore $m_{\text{bol}} - m_{\text{i}} \approx -1.9$ mag and $m_{\text{bol}} - m_{\text{z}} \approx -2.2$ mag. We assume that these corrections are constant in time and apply them to the bolometric light curves to generate $i$- and $z$-band light curves (Figure 2).

@@

\subsection{AGN Variability}
\label{sec:ch2_agns}
We also consider short-duration optical variability from active galactic nuclei (AGNs). AGN typically show strong variability on month or year-long timescales, making AGN outbursts too long in duration to be confused with a kilonovae. However, recent work has detected rare cases of day-long  or shorter variability in the NIR. \citet{Genzel+03} observed an H-band flare in Sgr A$^{*}$ during which the source brightened by a factor of 5. This flare lasted $\sim$ 30 min, with a characteristic rise time of $\sim2-5$ min. Such short timescale flares can be ruled out as kilonova contaminants by requiring a detection on more than a single night. Flares with longer durations are also unlikely to be significant contaminants. \citet{Totani+05} performed {\em V}- and {\em i}-band observations of six AGN, selected on the basis of their variability, over a period of four days. They found typical variability of only $\sim1-5\%$ above their host galaxy luminosity. More recent work by \citet{Ruan+12} studied the variability of a sample of \fermi selected blazars. They found that these sources showed a typical rms variability of $\sim0.6$ mag on timescales of $\sim 10$ d. Therefore, AGN are unlikely to exhibit sufficiently large variability to be confused with a kilonova.

@@

So far, we have only considered kilonova models affected by the large opacities of r-process heavy nuclei. We now consider the effects of modifications to the standard kilonova models and their impact on our detectability results. The key issue in determining the nature of kilonova emission is the electron fraction, $Y_e$. The value of $Y_e$ in the dynamical ejecta and from accretion disk winds is low $(Y_e \lesssim 0.2)$ which leads to the production of r-process nuclei and strong suppression of the optical emission. However, if the electron fraction of the ejecta is above the critical value of $Y_e \approx 0.25$, r-process nucleosynthesis is not able to produce heavy elements \citep[particularly the lanthanides][]{Kasen+15}. The resulting opacities will be closer to those from the Fe-peak elements, leading to a bluer transient. Here we investigate speculative scenarios that could produce a ``blue" kilonova component and assess their impact on {\em r}-band detectability.

@@

Recent work by \citet{Fernandez+15} found that the amount of ejected mass is a function of the spin of the remnant black hole, with more rapidly spinning black holes leading to higher ejecta masses by a factor of several. Furthermore, they found that $Y_{{\rm e}}$ increased monotonically with black hole spin due to an increased early-time neutrino luminosity from a rapidly spinning black hole. They found that in the most extreme cases $(a \gtrsim 0.8)$, the system could eject $\sim10^{-5} - 3\times10^{-3}\;M_{\odot}$ of material with $Y_{{\rm e}} \gtrsim 0.25$. Specifically, an ejecta mass of $\sim10^{-3}\;M_{\odot}$ will produce a blue component in the kilonovae light curve with $\nu L_{\nu} \approx 7.5\times10^{40}$ erg s$^{-1}$ at $\sim6500$ \AA \; ($r \approx 22.5$ mag at 200 Mpc) and a peak time of $\lesssim$ 1 day \citep{Kasen+15}. This is significantly brighter in $r$-band than the kilonovae models discussed previously, but the short timescales make observing this component challenging.

\subsection{A Long-Lived Hyper-massive Neutron Star}
\label{sec:ch2_HMNS}
Another modification can be caused by a  surviving hyper-massive neutron star (HMNS). The HMNS is a potential result of NS-NS mergers, but in simulations it often collapses rapidly $(t \lesssim 100$ ms) to form a black hole \citep{Sekiguchi+11}. The prompt formation of a black hole is an implicit assumption in the kilonova models discussed so far in this paper. However, if the total mass of the binary is less than a critical value, the HMNS can survive for a longer period of time \citep{Bauswein+13a,Kaplan+14}. In this scenario, the resulting neutrino luminosity will raise the electron fraction of the disk wind ejecta and will suppress r-process nucleosynthesis. Thus, the lanthanide-free disk wind material will produce a brighter, bluer, and shorter lived component in the kilonova light curve \citep[see e.g.,][and references therein]{MetzgerPiro14,MetzgerFernandez14}. This emission component will have a strong viewing angle dependence, with the polar regions being more strongly irradiated by neutrinos than the equatorial regions which will remain obscured by lanthanide-rich material. Consequently, the blue early component is more pronounced when the merger is observed along the polar axis.

@@

\subsection{A Neutron Precursor}
\label{sec:ch2_neutronpre}
Lastly, we consider the case in which a small fraction of the neutron-rich ejecta is expanding so rapidly that it avoids the initial phase of {\em r}-process nucleosynthesis. This effect has been seen in several general relativistic simulations \citep{Bauswein+13b,Goriely+15,Just+15}. In particular, \citet{Bauswein+13b} found that for a small fraction of the ejecta $(\sim 10^{-5} - 10^{-4}\; M_{\odot})$, the expansion timescale was sufficiently rapid $(\lesssim 5$ ms) that they evade neutron capture. These neutrons will undergo $\beta$-decay and release energy into the ejecta. Given that the photon diffusion time is on the order of a few hours in the outer layers of the ejecta, a significant fraction of this energy will manage to produce radiation. The light curves of this ``neutron precursor" were modeled by \citet{Metzger+15}. They found that the $\beta$-decay from the population of free neutrons at the leading edge of $10^{-4}\;M_{\odot}$ of ejecta can produce a transient with a timescale of $\sim1-2$ hours and a peak {\em r}-band magnitude of $\approx 22.2$ mag at 200 Mpc.

@@

\begin{deluxetable}{cccccccccc}
\tabletypesize{\footnotesize}
\tablecolumns{9}
\tabcolsep0.05in\footnotesize
\tablewidth{0pt}
\tablecaption{Follow-up Capabilities of Wide-Field Telescopes}
\tablehead{\multicolumn{3}{c}{} & \multicolumn{2}{c}{{\em r}-band} & \multicolumn{2}{c}{{\em i}-band} & \multicolumn{2}{c}{{\em z}-band} & \multicolumn{1}{c}{} \\
\colhead{Instrument} & \colhead{FoV} & \colhead{Etendue} & \colhead{Exp.} & \colhead{Rate}  & \colhead{Exp.}  &\colhead{Rate} & \colhead{Exp.} & \colhead{Rate} &  \colhead{$i + z$ Rate} \\
\colhead{} & \colhead{(deg$^2$)} & \colhead{(m$^2$ deg$^2$)} & \colhead{(s)} & \colhead{(deg$^2$ hr$^{-1}$)} & \colhead{(s)} & \colhead{(deg$^2$ hr$^{-1}$)} & \colhead{(s)} & \colhead{(deg$^2$ hr$^{-1}$)} &  \colhead{(deg$^2$ hr$^{-1}$)}}
\startdata
DECam$^{{\rm a}}$ & 3 &  37.7 & 4200 & 2.5 & 250 & 43 & 150 & 72 & 27  \\
ZTF$^{{\rm b}}$ & 47 & 53.2 & $9\times10^5$  & 0.2 & 1.6$\times10^4$ & 10 & {\bf --} & {\bf --}  & {\bf --}   \\
Subaru HSC$^{{\rm c}}$  & 1.8  & 90.5 & 520 & 12 & 55 & 115 & 45 & 145 & 65 \\
Pan-STARRS2$^{{\rm d}}$ & 14 & 35.6 & $1.4\times10^4$  & 4 & 700  & 72 & 350 & 144  & 30 \\
LSST$^{{\rm e}}$ & 9.6 & 315 & 390 & 88 & 28 & 1235  & 19 & 1820 & 735
\enddata
\tablecomments{Expected rates of sky coverage in deg$^2$ hr$^{-1}$ for several existing and future wide-field facilities at a depth of $r\approx26$ mag, $i\approx24$ mag and $z\approx23$ mag (i.e., the depths necessary to achieve a 95\% detection rate for kilonovae). We note that for HSC and LSST we include overhead times of 20s and 2s, respectively, as they are comparable to the exposure times.
References: \begin{enumerate}[label=\alph*,topsep=5pt]
\item DECam ETC, \url{http://www.ctio.noao.edu/noao/content/Exposure-Time-Calculator-ETC-0}
\item \citet{Nissanke+13,KasliwalNissanke14}
\item HSC ETC, \url{http://www.naoj.org/cgi-bin/img_etc.cgi}
\item Pan-STARRS DRM, \url{http://pan-starrs.ifa.hawaii.edu/}
\item LSST ETC, \url{http://dls.physics.ucdavis.edu:8080/etc4_3work/servlets/LsstEtc.html}
\end{enumerate}
}
\label{tab:ch2_tele}
\end{deluxetable}
